---
title: "Nanofish: Multivariada"
# AChE activity 1        CAT activity 2         GPx activity 3     GSH content 4  
# GST activity 5         Lipid peroxidation 6    ROS levels 7       SOD activity 8
# *Motor function: Distance  9                 Sensory-motor function: Distance 10 
# Predatory performance 11        [Feeding time 12]       [Speed during feeding 13]
# rodar para sensory-motor function; 
output:
  html_document:
    cache: false
    df_print: paged
    mathjax: "cdn"
bibliography: references.bib
---

# Set up environment

## Load libraries

```{r global options, warning=FALSE, include=FALSE}
pacman::p_load(knitr,
               rmdformats,
               metafor,
               dplyr,
               ggalluvial,
               orchaRd, #https://rdrr.io/github/daniel1noble/orchaRd/f/README.md
               GGally,
               patchwork,
               formatR,
               emmeans,
               clubSandwich)

## Global options~çjk
knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, prompt = FALSE,
  tidy = TRUE, comment = NA,
  message = FALSE, warning = FALSE
)
```

## Load functions

```{r load functions, include=FALSE}
source("bubble_plot.R",encoding = "UTF-8") # adicionado controles para cores por variável categórica, mesmo em gráficos sem o parâmetro "by" na função bubble_plot
source("var.comp.R",encoding = "UTF-8") # alterado para multinível de 4 níveis
source("diagnostic_plots.R",encoding = "UTF-8") 
source("influentialcases_plots.R",encoding = "UTF-8")

# extract values for report in R markdown
extract_report <- function(m, outcome, RE_formula) {
  assign("re_formula", deparse(RE_formula), envir = .GlobalEnv)
  assign("beta", m$beta, envir = .GlobalEnv)
  assign("se", m$pi$se, envir = .GlobalEnv)
  assign("tval", m$pi$tval, envir = .GlobalEnv)
  assign("ci_lb", m$pi$ci.lb, envir = .GlobalEnv)
  assign("ci_ub", m$pi$ci.ub, envir = .GlobalEnv)
  assign("pi_lb", m$pi$pi.lb, envir = .GlobalEnv)
  assign("pi_ub", m$pi$pi.ub, envir = .GlobalEnv)
  assign("I2_Total", round(m$i2[1], 2), envir = .GlobalEnv)
  assign("QE", m$QE, envir = .GlobalEnv)
  assign("QEp", if (m$QEp < 0.001) "< 0.001" else paste("=", round(m$QEp, 3)), envir = .GlobalEnv)
  
  sigma2_text <- paste0("$\\sigma^2_{", sub(".*/", "", m$s.names), "} = ", sprintf("%.2f", m$sigma2), "$", collapse = ", ")
  assign("sigma2", sigma2_text, envir = .GlobalEnv)
}

additional_results <- function(m) {
  
  m[["i2"]] <- i2_ml(m)
  
  if (is.null(m$formula.mods)) {
    m[["pi"]] <- predict(m, digits = 2)
  }
  
  m[["icc"]] <- round(m$sigma2 / sum(m$sigma2), 3)
  
  return(m)
}
```

## Load data

```{r Load data, include=FALSE}
file <- "mvMetaAnalysis_export.csv"

df_original <- read.csv(file,  header = TRUE, stringsAsFactors = TRUE, na.strings = c("NA"))

# EScluster    = control group cluster
# StudyCluster = resercher net cluster

# create individual id for each ES
df_original$ESid <- rep("ES", nrow(df_original))
df_original$ESid <- paste(df_original$ESid, c(1:nrow(df_original)), sep = "")


outcomeslist = c("AChE activity", 
                 "CAT activity",
                 "SOD activity",
                 "GPx activity",
                 "GST activity",
                 "GSH content",
                 "ROS levels",
                 "Lipid peroxidation",
                 "Sensory-motor function",
                 "Motor function",
                 "Predatory performance",
                 "Speed during feeding",
                 "Feeding time")

# check classes
str(df_original)
```

### Adjust classes and transformations

```{r Adjust classes and transformations, echo=FALSE}
# adjust classes
df_original$StudyID      <- factor(df_original$StudyID)
df_original$StudyCluster <- factor(df_original$StudyCluster)
df_original$EScluster    <- factor(df_original$EScluster)
df_original$ParticleShape<-factor(sub(".* ", "",df_original$ParticleShape)) #remove numbers
df_original$DevelopmentalStage<-factor(
      sub(".* ", "", df_original$DevelopmentalStage), # remove numbers
      levels = c("Embrio","Larva","Juvenile","Adult","Unclear"))
df_original$Outcome <- factor(df_original$Outcome,
                              levels = outcomeslist)

# numeric variables transformation
# df_original$ExposureDurationDays<-log10(df_original$ExposureDurationDays+1) 
# df_original$Concentration_mg_L  <-log10(df_original$Concentration_mg_L+1) 
# df_original$ParticleSizeMean    <-log10(df_original$ParticleSizeMean+1)

str(df_original)
```

### Calculate Effect Size

```{r effect size, echo=TRUE}
df_original <- metafor::escalc(measure = "SMD", 
             n1i = n_treat, 
             n2i = n_ctrl, 
             m1i = mean_treat, 
             m2i = mean_ctrl, 
             sd1i = STD_treat, 
             sd2i = STD_ctrl, 
             data = df_original, vtype = "UB") 
write.csv(df_original,file = "mvMetaAnalysis_SMDs.csv")
```

### Create variables

```{r create variables, echo=TRUE}
mRF <- list() # random effects formula investigation models
mRE <- list() # random effects multilevel models
mMR <- list() # multilevel metaregression models

colormap <-c("Embrio" = "khaki", 
            "Larva" = "lightgreen", 
            "Juvenile" = "lightskyblue", 
            "Adult" = "salmon", 
            "Unclear" = "plum",
            "ExposureDurationDays"= "cornflowerblue",
            "ParticleSizeMean"= "chartreuse4",
            "Concentration_mg_L"= "#fa0079ff",
            "Aminoplast" = "chocolate4",
            "LDPE" = "#2200faff",
            "PE" = "#0089faff",
            "PET" = "#00faedff",
            "PLA" = "#00fa29ff",
            "PS" = "#faf200ff",
            "PVC" = "#fa9a00ff",
            "Publication year"="black",
            "Variance"="navyblue")
```

# Multinível
```{r}
for (outcome in outcomeslist){
  df <- df_original[ which(df_original$Outcome == outcome ),]
  print(outcome)
  m <- rma.mv(yi, vi, 
              random = ~ 1 | Study/EScluster/ESid,
              data=df, method="ML")
  
  nSt <- m$s.nlevels[1] # number of studies
  nEC <- m$s.nlevels[2] # number of ESclusters
  nES <- m$s.nlevels[3] # number of independent ES (OBS: there is no repeated measurements included)
  
  if (nES == nSt){ 
    RE_formula = formula(~1 | Study) # one ES by Study
  } else if (nEC>nSt & nEC<nES){ 
    RE_formula = formula(~1 | Study/EScluster/ESid) # more than one EScluster by Study
  } else{
    RE_formula = formula(~1 | Study/ESid) # only one EScluster by Study
  }
  
  if (nES == nSt){
    VCVrho <- 0
    VCV <- df$vi
  } else {
    VCVrho <- 0.5
    VCV <- vcalc(vi, cluster = interaction(df$EScluster,df$Study), obs = ESid, data = df, rho = VCVrho)
  }
  
  mname1 <-outcome
  mname2 <-paste0(mname1,"_RobVar")
  
  mRE[[mname1]] <- rma.mv(yi, VCV,random = RE_formula,
                          data=df,slab = Study, method="REML",test="t", 
                          dfs="contain", level=95)
  mRE[[mname1]] <- additional_results(mRE[[mname1]])
  
  mRE[[mname2]] <- robust(mRE[[mname1]], cluster = df$Study, clubSandwich = TRUE)
  
  mRE[[mname2]] <- additional_results(mRE[[mname2]])
  
  summary(mRE[[mname2]])
  I2_ML_RobVar<-i2_ml(mRE[[mname2]])
  I2_ML_RobVar
  mRE[[mname2]][["i2"]]
  mRE[[mname2]][["pi"]]
  mRE[[mname2]][["icc"]]
  
}
```
## Orchard

```{r echo=TRUE}
colormap1 <-c("AChE activity" = "#ff65acff", 
            "CAT activity" = "#f962ddff", 
            "GPx activity" = "#d575feff", 
            "GSH content" = "#8b93ffff", 
            "GST activity" = "#00acfcff",
            "Lipid peroxidation"= "#00bbdaff",
            "ROS levels"= "#00c1abff",
            "SOD activity"= "#00be70ff",
            "Motor function" = "#24b700ff",
            "Sensory-motor function" = "#8cab00ff",
            "Predatory performance" = "#be9c00ff",
            "Feeding time" = "#e18a00ff",
            "Speed during feeding" = "#f8766dff"
            )

p <-list()
for (n in 1:length(outcomeslist)){
  mname1 <-outcomeslist[[n]]
m <- mRE[[paste0(mname1,"_RobVar")]]
I2<-i2_ml(m)
  
if (n<=8){
scalerange<-c(-30,30)
}else{
  scalerange<-c(-11,13)
}

p[[n]]<-orchard_plot(m, mod = "1", xlab = "Effect size", group = "Study", k = TRUE, g = TRUE, transfm = "none", angle = 0,legend.pos = "top.out") + 
   annotate(geom = "text", x = 0.6, y = 5, label = paste0("italic(I)^{2} == ", round(I2[1],1), "*\"%\""), color = "black", parse = TRUE, size = 3) +
  scale_x_discrete(labels = c(outcomeslist[[n]])) +
  scale_fill_manual(values = colormap1[[n]]) +
  scale_colour_manual(values = colormap1[[n]])+
  scale_size_continuous(range = c(1, 7), limits = c(0.1, 8), labels = scales::number_format(accuracy = 0.1))+
  scale_y_continuous(limits = scalerange)+
  theme(legend.position = "right" ,
          axis.title.x = element_blank())
}
 
layout <- " A
            B
            C
            D
            E
            F
            G
            H
             "
Reduce('+', p[1:8]) + plot_layout(design = layout)
Reduce('+', p[9:length(outcomeslist)]) + plot_layout(design = layout)


```

# Multivariada
## Alluvial plot
```{r echo=FALSE}
colormap <-c("Embrio" = "khaki", 
            "Larva" = "lightgreen", 
            "Juvenile" = "lightskyblue", 
            "Adult" = "salmon", 
            "Unclear" = "plum",
            "ExposureDurationDays"= "cornflowerblue",
            "ParticleSizeMean"= "chartreuse4",
            "Concentration_mg_L"= "#fa0079ff",
            "Aminoplast" = "chocolate4",
            "PE" = "#0089faff",
            "PET" = "#00faedff",
            "PLA" = "#00fa29ff",
            "PS" = "#faf200ff",
            "PVC" = "#fa9a00ff",
            "Publication year"="black",
            "Variance"="navyblue")
### draw an alluvial plot to show the heterogeneous experimental designs of the studies included in the meta-analysis

#make a dataframe of frequencies for selected variables
freq <- as.data.frame(table(df_original$DevelopmentalStage, df_original$ExposureDurationCat, df_original$ParticleSizeCat, df_original$ParticleMaterial)) %>%
    dplyr::rename(Stage = Var1, Duration = Var2,Size = Var3, Material = Var4)

# Check for proper data to plot
#ggalluvial::is_alluvia_form(as.data.frame(freq), axes = 1:4, silent = FALSE)

ggplot(data = freq, aes(axis1 = Stage, axis2 = Duration,  axis3 = Size, axis4 = Material, y = Freq)) + 
    geom_alluvium(aes(fill = Stage, colour = Stage)) + 
    scale_color_manual(values = colormap)+
    scale_fill_manual(values = colormap)+
    geom_flow() + 
    geom_stratum() + 
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
    theme_void() + 
    theme(legend.position = "none", 
          plot.title = element_text(hjust = 0, vjust = 3), 
          axis.title.x = element_text(), axis.text.x = element_text(face = "bold"), 
          plot.margin = unit(c(1, 1, 0, 1), "cm")
          ) + 
  scale_x_discrete(limits = c("Dev. stage", "Duration", "Size","Material"), position = "top")
# save fig as .png
# png(filename = "./alluvil_plot.png", width = 8, height = 4, units = "in", type = "windows", res = 400)
# alluvil_plot
# dev.off()
```

```{r, echo=FALSE}
#pdf(file='Figures/Boxplot_ESbyOutcome.pdf') # Open SVG device with specific file name
df_original %>%
  mutate(class = factor(Outcome, levels = rev(levels(Outcome)))) %>%
  ggplot( aes(yi, class, fill=class))+ 
    geom_boxplot() +
    xlab("ES") + 
    ylab("") +
    theme_bw(base_size = 18) +
    theme(legend.position="none")
#dev.off() 
```

## Models
OBS: Results are not appropriate because it is not possible to include multilevel structure, but... if I calculate vcalc already considering the different levels of correlations?

```{r}
#https://metafor-project.org/doku.php/analyses:berkey1998

MV<-list()

VCVrho<-0.5

VCV <- vcalc(vi, cluster = Study, type=Outcome, grp1=ESid, grp2=EScluster, w1=n_treat, w2=n_ctrl, data = df_original, rho = VCVrho)

MV[[1]] <- rma.mv(yi, VCV,random = ~ Outcome | Study, mods= ~  0 + Outcome,
                        data=df_original,slab = Study, method="REML",test="t",
                        dfs="contain", level=95) 
MV[[2]] <- robust(MV[[1]], cluster = df_original$Study, clubSandwich = TRUE,verbose=TRUE)

df_original$Year_centered <- df_original$Year-mean(df_original$Year)
MV[[3]] <- rma.mv(yi, VCV,random = ~ Outcome | Study, mods= ~  0 + Outcome +
                 Outcome:(Year_centered + vi),
                        data=df_original,slab = Study, method="REML",test="t",
                        dfs="contain", level=95) 
MV[[3]] <- robust(MV[[1]], cluster = df_original$Study, clubSandwich = TRUE,verbose=TRUE)


MV[[4]] <- rma.mv(yi, VCV,random = ~ Outcome | Study, mods= ~  0 + Outcome +
                 Outcome:(ParticleSizeMean + ExposureDurationDays*DevelopmentalStage),
                        data=df_original,slab = Study, method="REML",test="t",
                        dfs="contain", level=95)

#save(MV, VCV, df_original, VCVrho, file = "MV_workspace.RData")
```
```{r}
print("Multivariate of outcomes")
summary(MV[[1]])
print("Multivariate of outcomes with robust variance")
summary(MV[[2]])
print("Multivariate of outcomes with publication bias correction")
summary(MV[[3]])
print("Multivariate of outcomes with moderators - concentration not included due to convergence issues")
summary(MV[[4]])
```

```{r}
#load("MV_workspace.RData")
```


# Referências

```{r}
# Referências
```
