---
title: "Nanofish_mv"
author: "Querusche"
date: "2025"
output:
  pdf_document: default
  html_document: default
  df_print: paged
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: inline
---

## Tutorials from:

-   Y. Yang, M. Macleod, J. Pan, M. Lagisz, S. Nakagawa, 2023. Advanced
    methods and implementations for the meta-analyses of animal models:
    current practices and future recommendations. Neurosci. Biobehav.
    Rev., 146 <https://doi.org/10.1016/j.neubiorev.2022.105016>

-   Yefeng Yang, Malcom Macleaod, Jinming Pan, Malgorzata Lagisz,
    Shinichi Nakagawa, 2022. The current practices of meta-analyses
    using animal models, and underappreciated opportunities using
    advanced methods: multilevel models and robust variance estimation.
    Neuroscience & Biobehavioral Reviews.
    [https://doi.org/10.1016/j.neubiorev.2022z.105016](https://doi.org/10.1016/j.neubiorev.2022.105016){.uri}

-   Wolfgang Viechtbauer <https://www.metafor-project.org>
    <https://wviechtb.github.io/metafor/reference/misc-recs.html>
    <https://wviechtb.github.io/meta_analysis_books/>

-   Shinichi Nakagawa, Malgorzata Lagisz, Rose E. O’Dea, Patrice
    Pottier, Joanna Rutkowska, Alistair M. Senior, Yefeng Yang, Daniel
    W.A. Noble. 2023. orchaRd 2.0: An R package for visualizing
    meta-analyses with orchard plots. Methods in Ecology and Evolution,
    <https://doi.org/10.1111/2041-210X.14152> (preprint = EcoEvoRxiv,
    <https://doi.org/10.32942/X2QC7>).
    <https://daniel1noble.github.io/orchaRd/>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = "H", out.extra = "")

devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
pacman::p_load(devtools, tidyverse, metafor, patchwork, R.rsp, orchaRd, emmeans,
    ape, phytools, flextable)

library(clubSandwich)
library(GGally)
library(ggplot2)
library(grid)
library(gridExtra)
library(pacman)
library(metafor)
library(dplyr)
library(tidyverse)
library(gt) # https://posit.co/blog/great-looking-tables-gt-0-2/
library(metacart)

```

## Preparing data

1 - load data 2 - configures factor and numeral variables 3 -
transformations of numeral variables

NA = not applicable Unclear = unavailable information on the paper

```{r Load data, echo=FALSE}

source("functions_Nanofish.R",encoding = "UTF-8")
m = vector("list",3)
names(m) <- c("null","forest","random_effects")

df_original<-load_prep_df("mvMetaAnalysis.csv")

datainfo <- summary(df_original)
# write.table(datainfo, "descriptives.txt", sep="\t")

variables <- variable.names(df_original)
outcomeslist = sort(unique(df_original$Outcome))
moderatorslist = c(   "Species",
                      "Sex",
                      "DevelopmentalStage",
                      "ParticleMaterial", 
                      "ParticleShape", 
                      "ParticleSizeMean",
                      "AdministrationRoute", 
                      "Concentration_mg_L",
                      "ExposureDurationDays")

outcomeslist
moderatorslist
```

## Calculate effect size

"SMD" for the standardized mean difference (Hedges, 1981) "SMDH" for the
standardized mean difference with heteroscedastic population variances
in the two groups (Bonett, 2008, 2009)

UB = to compute unbiased estimates of the sampling variances (equation 9
in Hedges, 1983)

```{r}
df_original <- escalc(measure = "SMD", 
             n1i = n_treat, #n of treatment group
             n2i = n_ctrl, #n of control group
             m1i = mean_treat, #mean of treatment group 
             m2i = mean_ctrl, #mean of control group
             sd1i = STD_treat, #sd of treatment group
             sd2i = STD_ctrl, #sd of control group
             data = df_original, vtype = "UB") 
write.csv(df_original,file = "mvMetaAnalysis_SMDs.csv")
```

## Descriptives plots

```{r echo=FALSE}
#ggpairs(df_original, mapping = aes(color = Shape, alpha = 0.3), columns = moderatorslist,title = "")

#pdf(file='Figures/Boxplot_ESbyOutcome.pdf') # Open SVG device with specific file name
df_original %>%
  mutate(class = factor(Outcome, levels = rev(levels(Outcome)))) %>%
  ggplot( aes(yi, class, fill=class))+ 
    geom_boxplot() +
    xlab("ES") + 
    ylab("") +
    theme_bw(base_size = 18) +
    theme(legend.position="none")
set_plot_dimensions(7, 7)
# dev.off()
```

# Random variables fitting

```{r}
n_outcome = 11

outcome<-as.character(outcomeslist[n_outcome])
df <- df_original[ which(df_original$Outcome == outcome ),]
df <- df[order(df$DevelopmentalStage,-df$yi),]

models = c("null", "Exp", "Study", "Study_Exp", "Cluster_Study_Exp")

mRF = vector("list",5) ; names(mRF) <- models
anova = vector("list",5) ; names(anova) <- models

### fit random-effects null model - 1 level
m$null[[outcome]] <- rma.mv(yi, vi, data=df, method="ML")

# 2 level model 1
m$Exp[[outcome]] <- rma.mv(yi, vi, random = ~ 1 | StudyCluster/Study/EScluster,
            data=df, sigma2=c(0,0,NA),method="ML")

# 2 level model 2
m$Study[[outcome]] <- rma.mv(yi, vi,random = ~ 1 | StudyCluster/Study/EScluster, 
            data=df, sigma2=c(0,NA,0), method="ML")

# 3 level model
m$Study_Exp[[outcome]] <- rma.mv(yi, vi, random = ~ 1 | StudyCluster/Study/EScluster, 
            data=df, sigma2=c(0,NA,NA), method="ML")

# 4 level model
m$Cluster_Study_Exp[[outcome]] <- rma.mv(yi, vi, random = ~ 1 | StudyCluster/Study/EScluster,
            data=df, sigma2=c(NA,NA,NA), method="ML")

anova(m$null[[outcome]], m$Exp[[outcome]])
anova(m$null[[outcome]], m$Study[[outcome]])
anova(m$Exp[[outcome]],  m$Study_Exp[[outcome]])
anova(m$Study[[outcome]],m$Study_Exp[[outcome]])
anova(m$Study_Exp[[outcome]],m$Cluster_Study_Exp[[outcome]])
```

```{r}

 # Select data
  df <- df_original[ which(df_original$Outcome==outcome ),]
  df <-df[order(df$DevelopmentalStage,-df$yi),]
  df <- select(df, c("Year", "Study", "EScluster", "ExposureDurationDays",
                "DevelopmentalStage", "ParticleSizeMean", "Concentration_mg_L",
                "n_ctrl","n_treat","yi", "vi"))
  df<- df[complete.cases(df),]
  
# 3 level model
m1$RE_REML[[outcome]]<-rma.mv(yi, vi, 
            random = ~ 1 | Study/EScluster, 
            mods = formula(~  DevelopmentalStage*ExposureDurationDays
                           +Concentration_mg_L
                           +ParticleSizeMean),
            data=df,
            method="REML")

m1$RERV_REML[[outcome]] <- robust(m1$RE_REML[[outcome]], cluster = Study, 
                                  clubSandwich = TRUE)

model <- m1$RERV_REML[[outcome]]

cat_model <- orchaRd::mod_results(model, group = "Study", mod = "DevelopmentalStage", N="n_treat")

orchaRd::orchard_plot(cat_model, xlab = "ES", angle = 0) 


cros_bubble <- orchaRd::mod_results(model, mod = "ExposureDurationDays", group = "Study", weights = "prop", by = "DevelopmentalStage")

orchaRd::bubble_plot(cros_bubble, group = "Study", mod = "ExposureDurationDays", xlab = "ExposureDurationDays", legend.pos = "top.left")


con_bubble <- orchaRd::mod_results(model, mod = "Concentration_mg_L", group = "Study", weights = "prop")

orchaRd::bubble_plot(con_bubble, group = "Study", mod = "Concentration_mg_L", xlab = "Concentration_mg_L", legend.pos = "top.left", k =TRUE, g=TRUE)

con_bubble <- orchaRd::mod_results(model, mod = "ParticleSizeMean", group = "Study", weights = "prop")

orchaRd::bubble_plot(con_bubble, group = "Study", mod = "ParticleSizeMean", xlab = "Concentration_mg_L", legend.pos = "top.left", k =TRUE, g=TRUE)
```

```{r}
# Select data
    df <- df_original[df_original$Outcome==outcome,]
    df <- df[which(!is.na(df$Concentration_mg_L)),]
    df <- df[order(df$DevelopmentalStage,-df$yi),]
    df$DevelopmentalStage <- as.numeric(df$DevelopmentalStage)
    df <- select(df, c("Year", "ExposureDurationDays","DevelopmentalStage"
                , "ParticleSizeMean", "Concentration_mg_L","yi", "vi"))
    
corr <- round(cor(df), 1)
ggcorrplot(corr, hc.order = TRUE, type = "lower", lab= TRUE, p.mat = cor_pmat(df),
     outline.col = "white",
     ggtheme = ggplot2::theme_gray,
     colors = c("#6D9EC1", "white", "#E46726"))

```

```{r}
res <- rma.mv(yi, vi, random = ~ 1 | study/esid, data=dat)
robust(res, cluster=study, clubSandwich=TRUE)

rho <- 0.6 # run sensitivity analysis varying this value
V <- vcalc(vi, cluster=study, grp1=group1, grp2=group2, w1=n_sz, w2=n_hc,
           obs=task.diff, rho=rho, data=dat)

res0 <- rma.mv(yi, vi, random = ~ 1 | study/esid, data=dat, sigma2=c(0,NA))
anova(res0, res)
res0 <- rma.mv(yi, vi, random = ~ 1 | study/esid, data=dat, sigma2=c(NA,0))
anova(res0, res)

rma.mv(yi, vi, mods = ~ pubstatus, random = ~ 1 | study/esid, data=dat)
rma.mv(yi, vi, mods = ~ year, random = ~ 1 | study/esid, data=dat)
rma.mv(yi, vi, mods = ~ deltype, random = ~ 1 | study/esid, data=dat)
rma.mv(yi, vi, mods = ~ year + deltype, random = ~ 1 | study/esid, data=dat)

### assume that the effect sizes within studies are correlated with rho=0.6
V <- vcalc(vi, cluster=study, obs=esid, data=dat, rho=0.6)
res <- rma.mv(yi, V, random = ~ 1 | study/esid, data=dat)
robust(res, cluster=study, clubSandwich=TRUE)
```

o facilitate the interpretation, it is advisable to transform the effect
back to a normal correlation. This can be done using the convert_z2r
function in the {esc} package:

library(esc)

convert_z2r(0.52)

i2 \<- var.comp(full.model)

summary(i2)

plot(i2)

Fitting a three-level model only makes sense when it represents the
variability in our data better than a two-level model. When we find that
a two-level model provides a fit comparable to a three-level
model, Occam’s razor should be applied: we favor the two-level model
over the three-level model, since it is less complex, but explains our
data just as well.

run sensitivity analysis varying values of rho

especially compared to RVE, which can lead to overly conservative
results in small samples

```{r}
#os resultados com o grupo inteiro de dados e só com os que vão para a mateanalise são equiparáveis?

#colocar + x é igual a mod =?

```
